### 2012-04-09 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: Corrections.

Generalization is based on replacing fragments (sequences of subelements of a given element) from the input XML data by regular expressions, thus, using metacharacters like (*, +, ?). To provide a wide set of DTD candidates, each sequence is processed several times using various values of input parameters. Due to the very large number of possible DTD candidates, the authors employ certain real-life motivated heuristics.

>>>>

Generalization is based on replacing fragments (sequences of subelements of a given element) from the input XML data by regular expressions, thus, using metacharacters like \texttt{*}, \texttt{+}, \texttt{?}. To provide a wide set of DTD candidates, each sequence is processed several times using various values of input parameters. Due to the very large number of possible DTD candidates, the authors employ certain real-life motivated heuristics.

### 2012-04-09 doc/theses/mikula/conclusion.tex
Master thesis: Corrections.

Finally, we proposed a simple way how to combine the inferred statements with existing grammar inferring methods of the XML schema inference and we implemented it using the jInfer framework. Thus, we created the first complete, ready-to-use, and extensible implementation of the XML schema inference exploiting XQuery queries besides XML data.

>>>>

Finally, we proposed a simple way how to combine the inferred statements with existing methods of the XML schema inference inferring initial grammar and we implemented it using the jInfer framework. Thus, we created the first complete, ready-to-use, and extensible implementation of the XML schema inference exploiting XQuery queries besides XML data.
